Exploring and Validating the Motives Behind API Evolution: A Case Study

### 2015-03-20 rmtw/a6/latex8.tex
Second version of data collection
removed ocmment

\subsection{Data Collection}
% • data collection procedures (e.g. interviews? survey? and sampling?) 
% The main form of data collection will be performed through code and documentation analysis (third degree aka independent). In addition to this analysis, interviews will be conducted. The main purpose of the interviews is to provide insight regarding RQ1.1, but also to support data triangulation.

% Explain how we will sample the interviewees. (Ask Imed how this will be done).

% It is importnat that we explain exactly why we chose the collection methods we did. It is also important htat we clearly explain which methods relate to which RQs.

% Also explain why for example questionnaire wasn't used.

% Interviews will be used for:
% Main: Verify our findings
% Sub1: Provide additional insight (find stuff we missed)
% SUb2: Get more info about the user of the api

%Explain that we have two versions of the API, old and new
%Explain about how we'll collect them, i.e. in tables and spreadsheets. Different versions etc
%Double inspection will be performed. Two steps, independently by each of us to reduce research bias and human error.

The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of accompanying  documentation. The source code was comprised of two versions of APIs which the company had developed. An older version which is currently released and a newer version which is soon to be deployed. Each version of the API had its own relevant documentation. The documentation provided explanations of the features offered by the API and illustrated some examples of its usage.

>>>>

\subsection{Data Collection}
The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of accompanying  documentation. The source code was comprised of two versions of APIs which the company had developed. An older version which is currently released and a newer version which is soon to be deployed. Each version of the API had its own relevant documentation. The documentation provided explanations of the features offered by the API and illustrated some examples of its usage.
